Unifying Lower Bounds on Prediction Dimension of Consistent Convex Surrogates

### 2021-10-26 cvx-flats-neurips21/cvx-flats.tex
flats: tweak informal lemma 1

\paragraph{Literature on consistency and calibration.}% \label{subsec:consistency}
%\bo{Citation help appreciated!} \jessie{\cite{fisher1922mathematical,zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex} -- these are the ones I know of that discuss consistency in slightly various forms.  I believe the definition we run with is most similar to \cite{ramaswamy2016convex}.}
%\jessiet{Make this subsection more concise?}
We focus on surrogate losses $L: \reals^d \times \Y \to \reals$ that are consistent, roughly meaning that minimizing $L$-loss corresponds to solving the target problem of interest.
We give informal definitions of consistency in \S~\ref{sec:informal-consis-implies-indir}, with formal definitions in \S~\ref{sec:consis-implies-indir}.
%Def.~\ref{def:consistent-ell-informal} informally; Def.~\ref{def:consistent-ell} formally
%,bartlett2006convexity
% (Def.~\ref{def:consistent-prop-informal} informally; Def.~\ref{def:consistent-prop}, \S~\ref{sec:consis-implies-indir} formally)

@@

\raft{Your edit was much better for that narrative -- I think this narrative might flow better though.}
As discussed above, notions of consistency have appeared in the literature with respect to target losses, and to target statistics / properties.
We give informal definitions of both notions here, with formal versions deferred to \S~\ref{sec:consis-implies-indir}.
Lemma~\ref{lem:consistent-loss-implies-prop} shows that, in fact, one can capture consistency with respect to a target loss as a special case of consistency with respect to a target property.
This observation allows us to translate consistency from Quadrant 1 to Quadrant 2, and from Quadrant 3 to Quadrant 4;
in particular, it will allow us to prove bounds for all four quadrants simultaneously.

@@

We can now state Lemma~\ref{lem:consistent-loss-implies-prop}, with proof deferred to \S~\ref{sec:consis-implies-indir}.

\begin{restatable}{lemma}{consistentlossimpliesprop}\label{lem:consistent-loss-implies-prop}
	Let a convex $\P \subseteq \simplex$ be given.
	Given a surrogate loss $L \in \L$, link $\psi$, and target loss $\ell$, set
	$\mu(r,p) := \E_p \ell(r,Y) - \min_{r'}\E_p \ell(r',Y)$.
	Then there is a $\D$ such that
	$(L, \psi)$ is $\D$-consistent with respect to $\ell$ if and only if $(L,\psi)$ is $(\propdis, \D)$-consistent with respect to $\gamma := \prop{\ell}$. 
%	\btw{Note: don't actually need $\gamma$ nonempty here.}
\end{restatable}
\jessiet{Note: this is the formal version- do we want an informal version here instead, or to just leave the details in here?}

>>>>

\paragraph{Literature on consistency and calibration.}% \label{subsec:consistency}
%\bo{Citation help appreciated!} \jessie{\cite{fisher1922mathematical,zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex} -- these are the ones I know of that discuss consistency in slightly various forms.  I believe the definition we run with is most similar to \cite{ramaswamy2016convex}.}
%\jessiet{Make this subsection more concise?}
We focus on surrogate losses $L: \reals^d \times \Y \to \reals$ that are consistent, roughly meaning that minimizing $L$-loss corresponds to solving the target problem of interest.

We give informal definitions of consistency in \S~\ref{sec:informal-consis-implies-indir}, with formal definitions in \S~\ref{sec:consis-implies-indir}.
%Def.~\ref{def:consistent-ell-informal} informally; Def.~\ref{def:consistent-ell} formally
%,bartlett2006convexity
% (Def.~\ref{def:consistent-prop-informal} informally; Def.~\ref{def:consistent-prop}, \S~\ref{sec:consis-implies-indir} formally)

@@

As discussed above, notions of consistency have appeared in the literature with respect to target losses, and to target statistics or properties.
We give informal definitions of both notions here, with formal versions deferred to \S~\ref{sec:consis-implies-indir}.

@@

Lemma~\ref{lem:consistent-loss-implies-prop} in \S~\ref{sec:consis-implies-indir} shows that, in fact, one can capture consistency with respect to a target loss as a special case of consistency with respect to a target property.
Specifically, given a target loss $\ell$, one can take $\gamma = \prop{\ell}$ and define $\mu(r,p) := \E_p \ell(r,Y) - \min_{r'}\E_p \ell(r',Y)$ to be the $\ell$-regret of the report $r$.
This observation allows us to translate consistency from Quadrant 1 to Quadrant 2, and from Quadrant 3 to Quadrant 4;
in particular, it will allow us to prove bounds for all four quadrants simultaneously.
